A Fast kNN Algorithm Using Multiple Space-Filling Curves

### 2022-03-21 2022/Sensors/sensors.tex
two new references

%=================================================================
\documentclass[sensors,article,submit,moreauthors,pdftex]{Definitions/mdpi}

@@

The $k$ nearest neighbours (kNN) method is based on the following simple rule: an object is considered to belong to the class to which most of its nearest neighbours belong. Here, "neighbours" refers to objects that are close (in one sense or another) to the one being studied.
Note that in order to apply this method, some metric $L(\omega_i, \omega_j)$, i.e. the distance function, should be introduced in the feature space of objects. As a rule, the Euclidean distance is employed here, although other metrics may also be used [Gorban].

@@

As it was mentioned, the computational cost of searching for nearest objects increases with increasing dimensionality, both in the case of exhaustive search for all distances and when using tree structures. One mechanism for speeding up the search is dimensionality reduction, by reducing the problem of searching in a multidimensional space to the search in a one-dimensional space (over an interval). This is possible through the use of space-filling curves (Peano-Hilbert curves) that fill the multidimensional space. Such curves are used, for example, in multidimensional global optimization problems \cite{Strongin2018,Gergel2021}, in image processing \cite{Liang2008,Costa2012,Herrero2015}, etc.

>>>>

%=================================================================
\documentclass[entropy,article,submit,moreauthors,pdftex]{Definitions/mdpi}

@@

The $k$ nearest neighbours (kNN) method is based on the following simple rule: an object is considered to belong to the class to which most of its nearest neighbours belong. Here, "neighbours" refers to objects that are close (in one sense or another) to the one being studied.
Note that in order to apply this method, some metric $L(\omega_i, \omega_j)$, i.e. the distance function, should be introduced in the feature space of objects. As a rule, the Euclidean distance is employed here, although other metrics may also be used \cite{Mirkes2020}.

@@

As it was mentioned, the computational cost of searching for nearest objects increases with increasing dimensionality, both in the case of exhaustive search for all distances and when using tree structures. One mechanism for speeding up the search is dimensionality reduction, by reducing the problem of searching in a multidimensional space to the search in a one-dimensional space (over an interval). This is possible through the use of space-filling curves (Peano-Hilbert curves) that fill the multidimensional space. Such curves are used, for example, in global optimization \cite{Lera2015,Lera2018,Strongin2018,Gergel2021}, in numerical approximation of solutions to systems of nonlinear inequalities \cite{Lera2021}, in image processing \cite{Liang2008,Costa2012,Herrero2015}, etc.
